---
title: "Black Lives Matter - Analytics Dream Team"
author: "Adriana Ortiz, Enzo Novi Migliano, and Juan Zambrano"
output: html_notebook
---

# Abstract


The lives of African Americans have historically been disrespected. The treatment disparity of different ethnicities in the American society has a long and diverse scope. However, Under the following research question and problem statement: Do African Americans are significantly treated different in society than to other ethnicities in the United States? The presented study focused on the facets of the education, health, and law enforcement societal interaction. Through an archival analysis of governmental and public available data different statistical tests such as time series, linear and non-linear predictive models, and descriptive statistics will address the following hypothesis: **THe hypothesis are missing** . The current study provided great insight on the current situation of the Ethnical disparity of the American, as well possible solutions for the problem **We Need to make a better COnclusion**.


# Title of the Study

**WE NEED AN INTRODUCTION**


# Method

## Data

The data utilized in the analysis was collected from different reliable sources (e.g., government, news papers, Kaggle). The data was collected in throughout the months of September and October of 2020, and the files were uploaded into an online repository in the web server "GitHub" (link to the online repository:
https://github.com/EnzoNMigliano/Analytics-Dream-Team).


## Instruments

### SOftware

In order to perform the analysis of the data we utilized the software R(Version 4.0.2) [1], emulated in the Rstudio(Version 1.3.1073) [2]. In order to perform the version control of the documents throughout the study, the team utilized the Software Git [3] in connection with the server of GitHub [4].

### Packages

In order to perform the analysis of the data we utilized the following packages: Tidyverse [5], Corrplot [6], CaTools [7], caret [8], and forecast [9].

#### Installing Necessary Packages

The code below is with hash tags to prevent people from installing the packages twice. If your computer does not have one of the packages below, please take way the hash tag and install the package at your convenience.

```{r}

# install.packages("tidyverse")
# install.packages("corrplot")
# install.packages("caTools")
# install.packeges("caret")
# install.packages("forecast")

```


#### Loading Necessary Libraries

The code below will load the installed packages into your Rstudio.

```{r}
library(tidyverse)
library(corrplot)
library(caTools)
library(caret)
library(forecast)
```

### Loading Data sets for the analysis


```{r}
# Analytics-Dream-Team/Data

Covid_Deaths_Race <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/Provisional_COVID-19_Death_Counts_by_County_and_Race_CDC_OCT1.csv")

All_Illness_Deaths_Rate <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/Cumulative_Provisional_Counts_of_Deaths_by_Sex__Race__and_Age_CDC_AUG10.csv")

'2010&2011_Vadir_NY' <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/2014-2015_VADIR_INCIDENTS-CITY_OF_NEW_YORK.csv")

'2012&2013_Vadir_NY' <- 
  read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/2012-2013_VADIR_INCIDENTS-CITY_OF%20_NEW%20YORK.csv")

'2014&2015_Vadir_NY' <- 
  read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/2014-2015_VADIR_INCIDENTS-CITY_OF_NEW_YORK.csv")

# Analytics-Dream-Team/Data/BLM Diverse Data/police_info/

Police_Budget <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/police_info/budgets.csv")

Equipment_Police <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/police_info/dod_equipment_purchases.csv")

Contract_Police <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/police_info/police_contracts.csv")

Employment_FBI <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/police_info/police_employment_fbi.csv")

Police_Policies <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/police_info/police_policies.csv")

# Analytics-Dream-Team/Data/BLM Diverse Data/demographics/

Poverty_Census <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/demographics/poverty_census_bureau.csv")

Politics_538 <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/demographics/politics_538.csv")

Housing <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/demographics/housing.csv")

Eduction_Census <- read.csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/demographics/education_census_bureau.csv")

# Analytics-Dream-Team/Data/BLM Diverse Data/crime_data/

Juvenile_Arrests <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/crime_data/juvenile_arrests.csv")

NYPD_Arrests <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/crime_data/NYPD_Arrests_Data__Historic_.csv")

LA_Crime <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/crime_data/LA%20Crime_Data_from_2010_to_2019.csv")

Dallas_Arrests <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/crime_data/Dallas%20Police%20Arrests.csv")

Chicago_Crimes_2011topresent <- 
  read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/crime_data/Chicago%20Crimes_-_2001_to_Present.csv")

# Analytics-Dream-Team/Data/BLM Diverse Data/NYC_stop_frisk/

NY_StopFrisk_2015 <- 
  read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/NYC_stop_frisk/sqf-2015.csv")

NY_StopFrisk_2016 <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/NYC_stop_frisk/sqf-2016.csv")

NY_StopFrisk_2017 <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/NYC_stop_frisk/sqf-2017.csv")

NY_StopFrisk_2018 <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/NYC_stop_frisk/sqf-2018.csv")

NY_StopFrisk_2019 <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/NYC_stop_frisk/sqf-2019.csv")

Washington_post_Shootings <-
  read_csv("https://raw.githubusercontent.com/EnzoNMigliano/Analytics-Dream-Team/main/Data/shootings_wash_post.csv")

```

### Tidying the Data Sets

#### Tidying Enzo

**NYC SCHOOLS DATA**

In order to check if the data is tidy lets visualize the data set.

*2010-2011*

```{r}
View(`2010&2011_Vadir_NY`)
`2010&2011_Vadir_NY`
```

```{r}
summary(`2010&2011_Vadir_NY`)
```

*2012-2013*

```{r}
View(`2012&2013_Vadir_NY`)
`2012&2013_Vadir_NY`
```

```{r}
summary(`2012&2013_Vadir_NY`)

```

*2014-2015*

```{r}
View(`2014&2015_Vadir_NY`)
`2014&2015_Vadir_NY`
```

```{r}
summary(`2014&2015_Vadir_NY`)
```

All the New York Schools data sets are tidy, no further action required.


**All Illnesses DATA**

In order to check if the data is tidy lets visualize the data set.


```{r}
View(All_Illness_Deaths_Rate)
All_Illness_Deaths_Rate
```

```{r}
summary(All_Illness_Deaths_Rate)
```

This data set is tidy, no further action required.


**Chicago_Crimes**

In order to check if the data is tidy lets visualize the data set.


```{r}
View(Chicago_Crimes_2011topresent)
Chicago_Crimes_2011topresent
```


The Chicago Crimes 2011 to present is not Tidy yet. The variable "Date" has two values the date and time, as well as "Updated On". Therefore, we need to separate the values into two cells. One cell will be for the variable date and the other will be for the variable time. 

```{r}
# This code will fix the variable "Date"

ChicagoTidy <-
  Chicago_Crimes_2011topresent %>%
  separate(Date,
           into = c("Day",
                    "Time"),
           sep = " ")
```

```{r}
# This code will fiz the varible "Updated on"

ChicagoTidy2 <- ChicagoTidy %>%
  separate('Updated On',
           into = c("Updated_Date",
                    "Updated_Time"),
           sep = " ")
```

*The Tidy data set*

The tidy data set will be called ChigagoTidy2.



**Contracts with Police**

In order to check if the data is tidy lets visualize the data set.

```{r}
View(Contract_Police)
Contract_Police
```
```{r}
summary(Contract_Police)
```

This data set is tidy, no further action required.


**COVID Deaths**

In order to check if the data is tidy lets visualize the data set.


```{r}
view(Covid_Deaths_Race)
Covid_Deaths_Race
```


The Covid Deaths by Race data set is not tidy yet. THe data set has one one that contains observations which are actually name of other variables, three other variables to be precise. Also, the data set has a column with the values of the variables. Therefore, we need to transform the values of the column "Indicator" into three new columns.

```{r}

```





**Dallas Arrests**

In order to check if the data is tidy lets visualize the data set.

```{r}
View(Dallas_Arrests)
Dallas_Arrests
```


The Dallas Arrest Data set is not tidy yet. The data data set has some variables with two values in one cell. For example,  the observations of the variable "ArArrestDate" have two values per cell the day and the time. Therefore, we need to separate the values into to new complete variables. 

```{r}
# This code will fix all the variables "ArArrestDate" and "ArBkDate"

DallasArrestTidy <-
  Dallas_Arrests %>%
  separate(ArArrestDate,
           into = c("ArArrestDay",
                    "ArArrestTime"),
           sep = " ") %>%
  separate(ArBkDate,
           into = c("ArBkDay",
                    "ArBkTime"),
           sep = " ")
```

*The tidy data set*

The tidy data set will be called "DallasArrestTidy". In such data set, we transformed through the code above the variable (of the original data set) "ArArrestDate" into the variables "ArArrestDay" and "ArArrestTime" (in the tidy data set), also we the transformed the variable "ArBkDate" (of the original data set) into the variables "ArBkDay" and "ArBkTime" (in the tidy data set). see the new data set below:

```{r}
DallasArrestTidy
```




**Education Cencus**

In order to check if the data is tidy lets visualize the data set.

```{r}
View(Eduction_Census)
Eduction_Census
```


The data set Education Census is not tidy yet. There is one column that cointaing two different types of observations. The variable "Geographic.Area.Name" has three observations in it there is the name of the city, the State, and the classification of the city. Therefore, we need to separate those observations into completly new variables by assign it to new columns.

```{r}

```


*The tidy data set*



**Employment FBI**

In order to check if the data is tidy lets visualize the data set.


```{r}
View(Employment_FBI)
Employment_FBI
```

This data set is tidy, no further action required.




#### Tidying Juan 


#### Tidying Adriana


## Procedures


# Results


# conclusion


We need a conclusion.

# Refences


[1]  R Core Team (2020). R: A language and
  environment for statistical computing. R
  Foundation for Statistical Computing,
  Vienna, Austria. URL
  https://www.R-project.org/.
  
[2]

[3]

[4]

[5] Wickham et al., (2019). Welcome to the
  tidyverse. Journal of Open Source
  Software, 4(43), 1686,
  https://doi.org/10.21105/joss.01686

[6] Taiyun Wei and Viliam Simko (2017). R
  package "corrplot": Visualization of a
  Correlation Matrix (Version 0.84).
  Available from
  https://github.com/taiyun/corrplot


[7] Jarek Tuszynski (2020). caTools: Tools:
  Moving Window Statistics, GIF, Base64,
  ROC AUC, etc. R package version 1.18.0.
  https://CRAN.R-project.org/package=caTools

[8] Max Kuhn (2020). caret: Classification
  and Regression Training. R package
  version 6.0-86.
  https://CRAN.R-project.org/package=caret


[9] Hyndman R, Athanasopoulos G, Bergmeir C,
  Caceres G, Chhay L, O'Hara-Wild M,
  Petropoulos F, Razbash S, Wang E, Yasmeen F
  (2020). _forecast: Forecasting functions
  for time series and linear models_. R
  package version 8.13, <URL:
  https://pkg.robjhyndman.com/forecast/>.
  
  

