---
title: "Black Lives Matter - Analytics Dream Team"
author: "Adriana Ortiz, Enzo Novi Migliano, and Juan Zambrano"
output: html_notebook
---

**What should be in our R markdown**

R Code
Produce a R markdown of your analyses as a nb.html (not from knitr). 
Your code must contain title, authors, project abstract (problem statement, description, and conclusions), appropriate headings (#), detailed explanations of what each chunk does, and code chunks with comments.
Do not leave unused code in the file.



# Instaling Necessary Packages

```{r}
# install.package("tidyverse")

```


# Loading Necessary Libraries

```{r}
library(tidyverse)
```

# Loading Data sets for the analysis


```{r}
# Analytics-Dream-Team/Data

Covid_Deaths_Race <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/Provisional_COVID-19_Death_Counts_by_County_and_Race_CDC_OCT1.csv")

All_Illness_Deaths_Rate <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/Cumulative_Provisional_Counts_of_Deaths_by_Sex__Race__and_Age_CDC_AUG10.csv")

'2010&2011_Vadir_NY' <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/2014-2015_VADIR_INCIDENTS-CITY_OF_NEW_YORK.csv")

'2012&2013_Vadir_NY' <- 
  read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/2012-2013_VADIR_INCIDENTS-CITY_OF%20_NEW%20YORK.csv")

'2014&2015_Vadir_NY' <- 
  read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/2014-2015_VADIR_INCIDENTS-CITY_OF_NEW_YORK.csv")

# Analytics-Dream-Team/Data/BLM Diverse Data/police_info/

Police_Budget <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/police_info/budgets.csv")

Equipment_Police <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/police_info/dod_equipment_purchases.csv")

Contract_Police <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/police_info/police_contracts.csv")

Employment_FBI <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/police_info/police_employment_fbi.csv")

Police_Policies <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/police_info/police_policies.csv")

# Analytics-Dream-Team/Data/BLM Diverse Data/demographics/

Poverty_Census <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/demographics/poverty_census_bureau.csv")

Politics_538 <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/demographics/politics_538.csv")

Housing <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/demographics/housing.csv")

Eduction_Census <- read.csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/demographics/education_census_bureau.csv")

# Analytics-Dream-Team/Data/BLM Diverse Data/crime_data/

Juvenile_Arrests <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/crime_data/juvenile_arrests.csv")

NYPD_Arrests <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/crime_data/NYPD_Arrests_Data__Historic_.csv")

LA_Crime <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/crime_data/LA%20Crime_Data_from_2010_to_2019.csv")

Dallas_Arrests <- read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/crime_data/Dallas%20Police%20Arrests.csv")

Chicago_Crimes_2011topresent <- 
  read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/crime_data/Chicago%20Crimes_-_2001_to_Present.csv")

# Analytics-Dream-Team/Data/BLM Diverse Data/NYC_stop_frisk/

NY_StopFrisk_2015 <- 
  read_csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/NYC_stop_frisk/sqf-2015.csv")

NY_StopFrisk_2016 <- read.csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/NYC_stop_frisk/sqf-2016.csv")

NY_StopFrisk_2017 <- read.csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/NYC_stop_frisk/sqf-2017.csv")

NY_StopFrisk_2018 <- read.csv("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/NYC_stop_frisk/sqf-2018.csv")

NY_StopFrisk_2019 <- read.cvs("https://media.githubusercontent.com/media/EnzoNMigliano/Analytics-Dream-Team/main/Data/BLM%20Diverse%20Data/NYC_stop_frisk/sqf-2019.csv")

```

# conclusion
























