---
title: "Black Lives Matter - Analytics Dream Team"
author: "Adriana Ortiz, Enzo Novi Migliano, and Juan Zambrano"
output: html_notebook
---

**What should be in our R markdown**

R Code
Produce a R markdown of your analyses as a nb.html (not from knitr). 
Your code must contain title, authors, project abstract (problem statement, description, and conclusions), appropriate headings (#), detailed explanations of what each chunk does, and code chunks with comments.
Do not leave unused code in the file.

# Abstract
The lives of African Americans has historically been disrespeted. The disparity between the treatment of difererent races in the American society has a long scope. The problem has different facets and different implacaitons in day to day of a nation.

# Instaling Necessary Packages

```{r}
# install.packages("tidyverse")
# install.packages(corrplot)
# install.packages("caTools")
# install.packeges("caret")
# install.packages("forecast")

```


# Loading Necessary Libraries

```{r}
library(tidyverse)
library(corrplot)
library(caTools)
library(caret)
library(forecast)
```

# Loading Data sets for the analysis


```{r}
```

# conclusion